Articles_Plots

### 2022-04-09 Articles.Rmd
SMSE and model information stored as pdfs

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: X1, X2",Metric="MSE",
                                        All_MSE))

@@

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="MSE",
                                        All_MSE))

@@

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="MSE",
                                        All_MSE))

@@

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",
                                        All_MSE))

@@

```{r combine data and plot,fig.width = 18,fig.height = 10}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("Data Model: X1, X2",
                                          "Data Model: X1, X2, X1\u00B2",
                                          "Data Model: X1, X2, X2\u00B2",
                                          "Data Model: X1, X2, X1\u00B2, X2\u00B2"))

@@

Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
               "#DDCC77")

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
```

>>>>

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE))

@@

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE))

@@

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE))

@@

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE))

@@

```{r combine data and plot,fig.width = 8,fig.height = 12}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("Data Model: x\u2081, x\u2082",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))

@@

Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8","#E28490","#BB2C3E","#55141C",
               "#DDCC77")

@@

#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
```
